\thetitle

### 2021-05-17 writing/related.tex
edits to related work to fix monotoinc references discussion

The literature on gradual typing presents many semantics beyond the three used
here and two additional blame strategies.  Pyret (pyret.org) assigns fixed-size
data types the Natural semantics and functions a Transient semantics. The
Forgetful~\citep{cl-icfp-2017} and the Amnesic~\citep{gfd-oopsla-2019} semantics
are similar to Transient but use wrappers instead of in-lined checks.
Nom~\citep{mt-oopsla-2017} and other \emph{concrete\/}
semantics~\citep{wnlov-popl-2010, rsfbv-popl-2015, rzv-ecoop-2015,
rat-oopsla-2017} assume that every value comes with a type tag and use tag
checks to supervise the interactions between typed and untyped code.  Monotonic
references~\citep{svctg-esop-2015} and the semantics~\citep{tlt-popl-2019,
etg-icfp-19, tt-scp-20, tgt-popl-18, tt-sas-17} derived with the Abstracting
Gradual Typing technique~\citep{gct-popl-2016} are variants of Natural.  Among
these representative semantics, only Amnesic and Nom present innovative blame
strategies.  The experiment excludes these strategies because they seem to be
merely theoretical constructions and/or impose severe restrictions on
programmers.

>>>>

The literature on gradual typing presents many semantics beyond the three used
here and three additional blame strategies.  Pyret (pyret.org) assigns fixed-size
data types the Natural semantics and functions a Transient semantics. The
Forgetful~\citep{cl-icfp-2017} and the Amnesic~\citep{gfd-oopsla-2019} semantics
are similar to Transient but use wrappers instead of in-lined checks.
Nom~\citep{mt-oopsla-2017} and other \emph{concrete\/}
semantics~\citep{wnlov-popl-2010, rsfbv-popl-2015, rzv-ecoop-2015,
rat-oopsla-2017} assume that every value comes with a type tag and use tag
checks to supervise the interactions between typed and untyped code.  The semantics~\citep{tlt-popl-2019,
etg-icfp-19, tt-scp-20, tgt-popl-18, tt-sas-17} derived with the Abstracting
Gradual Typing technique~\citep{gct-popl-2016} are variants of Natural.
 Monotonic References~\citep{svctg-esop-2015, rsfbv-popl-2015, sfrbcsb-popl-2014, kas-pldi-2019} 
differ from Natural in the treatment of mutable data by
associating heap locations with a type and permitting only updates that 
make that type more precise.  
Among these representative semantics, only Amnesic, Nom and Monotonic References present innovative blame
strategies.  The experiment excludes the first because it is
merely a theoretical construction, the second because it imposes severe restrictions on
programmers and the third because it would require a complete
re-engineering of the Racket runtime. That said, the paper offers a
detailed chart that the creators of these blame strategies can transplant to their
linguistic setting and determine the value of their blame strategies.
